Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-25 paper/aldebaran.tex
font

We note that with the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathscr{N}(1.16,0.07)$ and metallicitiies $[\text{Fe}/\text{H}] \sim \mathscr{N}(-0.15,0.2)$ \citep{decin2003}  to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  %Using the scaling relations of \citep{eker2015}, we find that Aldebaran would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1} models, we compute the luminosity and radius evolution of the planet along the main sequence. $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 4.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.507 \pm 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 4.5~Gyr from $0.86 \pm 0.27$ to $1.55 \pm 1.0$ times that of the Earth today. Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, this planet and any of its moons may well have had temperate environments for some of their previous evolution, now long-since destroyed by their host star's evolution away from the main sequence.

>>>>

We note that with the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathcal{N}(1.16,0.07)$ and metallicitiies $[\text{Fe}/\text{H}] \sim \mathcal{N}(-0.15,0.2)$ \citep{decin2003}  to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  %Using the scaling relations of \citep{eker2015}, we find that Aldebaran would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1} models, we compute the luminosity and radius evolution of the planet along the main sequence. $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 4.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.507 \pm 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 4.5~Gyr from $0.86 \pm 0.27$ to $1.55 \pm 1.0$ times that of the Earth today. Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, this planet and any of its moons may well have had temperate environments for some of their previous evolution, now long-since destroyed by their host star's evolution away from the main sequence.
